Variability analysis

### 2022-06-21 experiment-2/analysis/stats/variability.Rmd
upload variability for exp2 / export R scripts
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r, echo = FALSE, fig.width = 6, fig.height = 1.2}
# Plot the whole sequence
ggline(ioi_art_seq_each, x = "Interval", y = "Mean", add = "mean_se", shape = "Condition", color = "Condition", xlab = "Interval", ylab = "IOIs (ms)", title = "IOI: Articulation") +
  geom_hline(yintercept = 188, linetype = "dotted") + # target tempo
  geom_vline(xintercept = c(8, 24, 49, 16, 41, 57), linetype = "twodash") + # transition points
  scale_x_continuous(breaks = seq(1,66,1))

ggline(ioi_dyn_seq_each, x = "Interval", y = "Mean", add = "mean_se", shape = "Condition", color = "Condition", xlab = "Interval", ylab = "IOIs (ms)", title = "IOI: Dynamics") +
  geom_hline(yintercept = 188, linetype = "dotted") + # target tempo
  geom_vline(xintercept = c(8, 24, 49, 16, 41, 57), linetype = "twodash") + # transition points
  scale_x_continuous(breaks = seq(1,66,1))
```

<!-- ### Each participant -->
<!-- ```{r, echo = FALSE, fig.width = 5, fig.height = 5} -->
<!-- # Plot the whole sequence for each participant -->
<!-- ggplot(ioi_art_seq_each, aes(x = Interval, y = Mean, color = SubNr)) + -->
<!--   geom_line() + geom_point() + facet_grid(Condition ~ .) + -->
<!--   geom_hline(yintercept = 188, linetype = "dotted") + # target tempo -->
<!--   geom_vline(xintercept = c(8, 24, 49, 16, 41, 57), linetype = "twodash") + # transition points -->
<!--   scale_x_discrete(breaks = seq(1,66,3)) + labs(x = "Interval", y = "IOIs (ms)", title = "IOI: Articulation") + theme_pubr() + theme(legend.position = "right") -->

<!-- ioi_dyn_seq <- ioi_dyn_seq_each[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), by = .(Condition, Skill, Interval)] -->
<!-- ggplot(ioi_dyn_seq_each, aes(x = Interval, y = Mean, color = SubNr)) + -->
<!--   geom_line() + geom_point() + facet_grid(Condition ~ .) + -->
<!--   geom_hline(yintercept = 188, linetype = "dotted") + # target tempo -->
<!--   geom_vline(xintercept = c(8, 24, 49, 16, 41, 57), linetype = "twodash") + # transition points -->
<!--   scale_x_discrete(breaks = seq(1,66,3)) + labs(x = "Interval", y = "IOIs (ms)", title = "IOI: Dynamics") + theme_pubr() + theme(legend.position = "right") -->
<!-- ``` -->

@@

ggplot(ioi_cv_subject, aes(x = Condition, y = MeanCV, color = Condition)) +
  geom_boxplot() +
  geom_point(aes(color = Condition)) +
  geom_line(aes(group = SubNr), size = 0.4, color = "black", alpha = 0.2) +
  facet_grid(. ~ Skill) +
  theme_pubr()
```

### Stats
- With Participant 2 (outside +/- 3SD)

@@

- Without Participant 2 (outside +/- 3SD)

```{r, echo = FALSE}
# descriptive stats
ioi_cv_subject[SubNr != 2, .(.N, MeanCV = mean(MeanCV), SDCV = sd(MeanCV)), by = .(Condition, Skill)]

aov_ez(id = "SubNr", dv = "MeanCV",
       within = c("Condition", "Skill"),
       data = ioi_cv_subject[SubNr != 2])
```

@@

ggplot(ioi_tra, aes(x = Condition, y = Mean, color = Condition)) +
  geom_boxplot() +
  geom_point(aes(color = Condition)) +
  geom_line(aes(group = SubNr), size = 0.4, color = "black", alpha = 0.2) +
  facet_grid(. ~ Skill) +
  theme_pubr()
```

@@

ggplot(ioi_tra_others, aes(x = Condition, y = Mean, color = Condition)) +
  geom_boxplot() +
  geom_point(aes(color = Condition)) +
  geom_line(aes(group = SubNr), size = 0.4, color = "black", alpha = 0.2) +
  facet_grid(Skill ~ Transition) +
  theme_pubr()
```

@@

add some postdoc comparisons...

>>>>

```{r, echo = FALSE, fig.width = 6, fig.height = 1.2}
# Plot the whole sequence
ggline(ioi_art_seq_each, x = "Interval", y = "Mean", add = "mean_se", shape = "Condition", color = "Condition", xlab = "Interval", ylab = "IOIs (ms)", title = "IOIs: Articulation") +
  geom_vline(xintercept = c(5, 17, 47, 8, 20, 39), linetype = "twodash") + # transition points
  scale_x_continuous(breaks = seq(1,66,1))

ggline(ioi_dyn_seq_each, x = "Interval", y = "Mean", add = "mean_se", shape = "Condition", color = "Condition", xlab = "Interval", ylab = "IOIs (ms)", title = "IOIs: Dynamics") +
  geom_vline(xintercept = c(5, 17, 47, 8, 20, 39), linetype = "twodash") + # transition points
  scale_x_continuous(breaks = seq(1,66,1))
```

<!-- ### Each participant -->
<!-- ```{r, echo = FALSE, fig.width = 5, fig.height = 5} -->
<!-- # Plot the whole sequence for each participant -->
<!-- ggplot(ioi_art_seq_each, aes(x = Interval, y = Mean, color = SubNr)) + -->
<!--   geom_line() + geom_point() + facet_grid(Condition ~ .) + -->
<!--   geom_hline(yintercept = 188, linetype = "dotted") + # target tempo -->
<!--   geom_vline(xintercept = c(8, 24, 49, 16, 41, 57), linetype = "twodash") + # transition points -->
<!--   scale_x_discrete(breaks = seq(1,66,3)) + labs(x = "Interval", y = "IOIs (ms)", title = "IOIs: Articulation") + theme_pubr() + theme(legend.position = "right") -->

<!-- ioi_dyn_seq <- ioi_dyn_seq_each[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), by = .(Condition, Skill, Interval)] -->
<!-- ggplot(ioi_dyn_seq_each, aes(x = Interval, y = Mean, color = SubNr)) + -->
<!--   geom_line() + geom_point() + facet_grid(Condition ~ .) + -->
<!--   geom_hline(yintercept = 188, linetype = "dotted") + # target tempo -->
<!--   geom_vline(xintercept = c(8, 24, 49, 16, 41, 57), linetype = "twodash") + # transition points -->
<!--   scale_x_discrete(breaks = seq(1,66,3)) + labs(x = "Interval", y = "IOIs (ms)", title = "IOIs: Dynamics") + theme_pubr() + theme(legend.position = "right") -->
<!-- ``` -->

@@

ggplot(ioi_cv_subject, aes(x = Condition, y = MeanCV, color = Condition)) +
  geom_boxplot() +
  geom_line(aes(group = SubNr), size = 0.4, color = "gray") +
  geom_point(aes(color = Condition)) +
  facet_grid(. ~ Skill) +
  theme_pubr()
```

### Stats
- With Participant 15 (outside +/- 3SD)

@@

- Without Participant 15 (outside +/- 3SD)

```{r, echo = FALSE}
# descriptive stats
ioi_cv_subject[SubNr != 15, .(.N, MeanCV = mean(MeanCV), SDCV = sd(MeanCV)), by = .(Condition, Skill)]

aov_ez(id = "SubNr", dv = "MeanCV",
       within = c("Condition", "Skill"),
       data = ioi_cv_subject[SubNr != 15])
```

@@

ggplot(ioi_tra, aes(x = Condition, y = Mean, color = Condition)) +
  geom_boxplot() +
  geom_line(aes(group = SubNr), size = 0.4, color = "gray") +
  geom_point(aes(color = Condition)) +
  facet_grid(. ~ Skill) +
  theme_pubr()
```

@@

ggplot(ioi_tra_others, aes(x = Condition, y = Mean, color = Condition)) +
  geom_boxplot() +
  geom_line(aes(group = SubNr), size = 0.4, color = "gray") +
  geom_point(aes(color = Condition)) +
  facet_grid(Skill ~ Transition) +
  theme_pubr()
```

@@

```{r export, include = FALSE}
knitr::purl("variability.Rmd")
```
